---
title: "preliminary_study"
author: "Filipe Cogo"
date: "17/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 
"//home/local/SAIL/filipe-cogo/wip-19-filipe-npm_greenkeeper_build_failures-scripts")
```

## Load external scripts

```{r load_external_scripts, echo=FALSE}

source("plotter.R")

```

## Load libraries

```{r load_libraries, include=FALSE, echo=FALSE}

library(data.table)
library(lubridate)
library(scales)
library(ggplot2)
library(stringr)
library(effsize)

```

## Read dataset

Reads two different data sets. While `releases` is the data about all package's releases, `dependencies` is the data about the dependencies of each package. Although `dependencies` also stores data about package's releases, any release of a package that has no valid dependency is not present in `dependencies`.

```{r read_data_set, include=FALSE, echo = FALSE}

issues = 
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_issues.csv",
        nThread = 80)

dependencies = 
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_dependencies_analysis.csv",
        nThread = 80)

init_pr = fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_first_pull_request.csv",
                nThread = 80)

package_names =
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_package_names.csv",
        nThread = 80)

print(paste("There are more package names than dependencies,",
            "since only packages with more than 100 commits",
            "are considered."))

```

# Link datasets

```{r link_dataset}


package_names[, package_id := 
                str_match(package_gh_url,
                          "^https://github\\.com/(.*?)/$")[,2]]

init_pr[, init_pr_id := 
          str_match(pr_repo_url,
                    "^https://api.github.com/repos/(.*?)$")[,2]]

issues[, issue_id := 
         str_match(issue_repo_url,
                    "^https://api.github.com/repos/(.*?)$")[,2]
         ]

dependencies[, client_name_id := 
               str_replace(client_name,
                           "@",
                           "/")]

```

How often are initial pull requests closed?

```{r}

# get initial pull requests
num_initial_pr = 
  nrow(init_pr)

# get closed initial pull requests
num_closed_initial_pr =
  nrow(init_pr[pr_state == "closed"])

# report proportion of closed initial pull request
paste(
  percent(
    num_closed_initial_pr / num_initial_pr
  ), "of the initial pull requests are eventually closed"
)

```

How much time do initial pull requests take to be closed?

```{r}

# get closed intial pull requests
closed_initial_pr =
  init_pr[pr_state == "closed"]

# calculate median time to merge an initial pull request
time_to_close_initial_pr =
  closed_initial_pr[,
                    .(pr_id,
                      time_to_close_initial_pr =
                        difftime(ymd_hms(pr_closed_at),
                                 ymd_hms(pr_created_at),
                                 units = "hours"))]

# report the median time to close the initial pull request
paste("The median time to close the initial pull request is",
      median(as.numeric(time_to_close_initial_pr$time_to_close_initial_pr)),
             "hours")

# plot the distribution
ggplot(time_to_close_initial_pr,
       aes(x = "",
           y = as.numeric(time_to_close_initial_pr))) +
  geom_violin(fill = "grey") +
  geom_boxplot(width = 0.05,
               fill = "white") +
  scale_x_discrete(name = "Initial PR") +
  scale_y_log10(name = "Time to close initial PR (hours)",
                labels = trans_format("log10", 
                                      math_format(10^.x))) +
  theme_classic() +
  theme(axis.ticks.x = element_blank())

print(paste("Five number summary for the time to close the initual pull request:"))
summary(as.numeric(time_to_close_initial_pr$time_to_close_initial_pr))

```

What is the proportion of open initial pull requests that are older than the median time to close the initial pull request?

```{r}

# get open initial PR
open_initial_pr =
  init_pr[pr_state == "open"]

# get latest date for open initial PR
latest_pr =
  max(open_initial_pr$pr_updated_at)

# calculate the life-time of the initial PR
open_initial_pr[, lifetime := 
                  difftime(ymd_hms(latest_pr),
                           ymd_hms(pr_updated_at),
                           units = "hours")]

# get the median time to close an initial PR
median_time_to_close_initial_pr =
  median(as.numeric(time_to_close_initial_pr$time_to_close_initial_pr))

paste(
  percent(
    nrow(open_initial_pr) /
      nrow(open_initial_pr[lifetime > 
                             median_time_to_close_initial_pr])
    ), "of the open initial pull request have a lifetime larger than",
  "the median time to close an initial pull request."
)


```

What is the difference between the time to merge an initial PR and the lifetime of open initial PR?

```{r}

# calculate median time to merge an initial pull request
time_to_close_initial_pr =
  closed_initial_pr[,
                    .(state = "closed",
                      time =
                        difftime(ymd_hms(pr_closed_at),
                                 ymd_hms(pr_created_at),
                                 units = "hours"))]

# calculate the life-time of the initial PR
lifetime_open_initial_pr = 
  open_initial_pr[, .(state = "open",
                      time = 
                        difftime(ymd_hms(latest_pr),
                                 ymd_hms(pr_created_at),
                                 units = "hours"))]

time_initial_pr.plot =
  rbind(time_to_close_initial_pr,
        lifetime_open_initial_pr)

time_initial_pr.plot$time =
  as.numeric(time_initial_pr.plot$time)

time_initial_pr.plot$state =
  factor(time_initial_pr.plot$state,
         levels = c("open",
                    "closed"),
         ordered = TRUE)
time_initial_pr.plot$x = ""

plot_violin(time_initial_pr.plot, 
            ycol = "time",
            xcol = "x",
            group = "state",
            split = TRUE) +
  scale_y_log10(name = "Lifetime (hours)",
                labels = trans_format("log10", 
                                      math_format(10^.x))) +
  scale_x_discrete(name = "Initial Pull-Request") +
  scale_fill_grey(name = "State",
                  start = 0.7,
                  end = 1,
                  breaks = c("closed",
                             "open"),
                  labels = c("Closed",
                             "Open"))+
  theme_classic()

```

How many dependencies do packages have when they integrate the Greenkeeper bot?

```{r}

# find the releases in which the bot was integrated
dependencies[, client_time := 
               ymd_hms(client_timestamp)]
closed_initial_pr[, initial_pr_time := 
                    ymd_hms(pr_closed_at)]

setkey(dependencies, 
       client_name_id,
       client_time)
setkey(closed_initial_pr,
       init_pr_id,
       initial_pr_time)

releases_initial_pr_was_closed = 
  dependencies[closed_initial_pr,
               roll = "nearest"]

releases_initial_pr_was_closed =
  releases_initial_pr_was_closed[!is.na(client_name)]

# get dependencies in releases in which the bot was integrated
dependencies_initial_pr_was_closed = 
  merge(dependencies,
        releases_initial_pr_was_closed,
        by.x = c("client_name",
                 "client_version",
                 "client_previous_version"),
        by.y = c("client_name",
                 "client_version",
                 "client_previous_version"))

# calculate the number of dependencies
num_dependencies_initial_pr_was_closed =
  dependencies_initial_pr_was_closed[, .(num_dependencies = .N),
                                     by = .(client_name,
                                            client_previous_version,
                                            client_version)]

summary(num_dependencies_initial_pr_was_closed$num_dependencies)

# find the releases in which the bot was not integrated
dependencies[, client_time := 
               ymd_hms(client_timestamp)]
open_initial_pr[, initial_pr_time := 
                    ymd_hms(pr_created_at)]

setkey(dependencies, 
       client_name_id,
       client_time)
setkey(open_initial_pr,
       init_pr_id,
       initial_pr_time)

dependencies[client_name_id %in% 
               unique(init_pr[pr_state == "open"]$init_pr_id),
             .GRP,
             by = client_name_id]

releases_initial_pr_is_open = 
  dependencies[open_initial_pr,
               roll = "nearest"]

releases_initial_pr_is_open =
  releases_initial_pr_is_open[!is.na(client_name)]

# get dependencies in releases in which the bot was integrated
dependencies_initial_pr_is_open = 
  merge(dependencies,
        releases_initial_pr_is_open,
        by.x = c("client_name",
                 "client_version",
                 "client_previous_version"),
        by.y = c("client_name",
                 "client_version",
                 "client_previous_version"))

# calculate the number of releases
num_dependencies_initial_pr_is_open =
  dependencies_initial_pr_is_open[, .(num_dependencies = .N),
                                     by = .(client_name,
                                            client_previous_version,
                                            client_version)]

summary(num_dependencies_initial_pr_is_open$num_dependencies)

# plot the differences

num_dependencies_initial_pr_is_open[, state := "open"]
num_dependencies_initial_pr_was_closed[, state := "closed"]

num_dependencies_initial_pr.plot = 
  rbind(num_dependencies_initial_pr_is_open,
        num_dependencies_initial_pr_was_closed)

num_dependencies_initial_pr.plot$state =
  factor(num_dependencies_initial_pr.plot$state,
         levels = c("open",
                    "closed"),
         ordered = TRUE)
num_dependencies_initial_pr.plot$x = ""

plot_violin(num_dependencies_initial_pr.plot, 
            ycol = "num_dependencies",
            xcol = "x",
            group = "state",
            trim = FALSE,
            split = TRUE) +
  scale_y_log10(name = "Number of dependencies",
                labels = trans_format("log10", 
                                      math_format(10^.x))) +
  scale_x_discrete(name = "Initial Pull-Request") +
  scale_fill_grey(name = "State",
                  start = 0.7,
                  end = 1,
                  breaks = c("closed",
                             "open"),
                  labels = c("Closed",
                             "Open"))+
  theme_classic()

wilcox.test(num_dependencies_initial_pr.plot[state == "closed"]$num_dependencies,
            num_dependencies_initial_pr.plot[state == "open"]$num_dependencies)
cliff.delta(num_dependencies_initial_pr.plot[state == "closed"]$num_dependencies,
            num_dependencies_initial_pr.plot[state == "open"]$num_dependencies)

print(paste("There is no evidence that the number of dependencies is",
            "different between packages that did and did not",
            "integrate the bot. I.e., the number of dependencies is",
            "not an important factor to determine whether the bot",
            "will be integrated or not."))
```

Do client packages perform more updates after using the bot?

```{r}

# find when the bot was integrated
closed_initial_pr[, initial_pr_time := 
                    ymd_hms(pr_closed_at)]

dependencies_before_after_init_pr =
  merge(dependencies,
        closed_initial_pr[,.(init_pr_id, 
                             initial_pr_time)],
        by.x = "client_name_id",
        by.y = "init_pr_id")

# flag releases that were published after and before bot integration
dependencies_before_after_init_pr[, event :=
                                    ifelse(
                                      difftime(
                                        ymd_hms(client_timestamp),
                                        initial_pr_time) > 0,
                                      "after_init_pr",
                                      "before_init_pr")]
# find number of upgrades in each release
num_dependencies_before_after_init_pr =
  dependencies_before_after_init_pr[, .(num_updates = 
                                          sum(dependency_resolved_version_change == "upgrade"),
                                        num_dependencies = .N),
                                    by = .(client_name_id,
                                           client_version,
                                           client_previous_version,
                                           event)]

# calculate proportion of updated dependencies
num_dependencies_before_after_init_pr[, proportion_updates :=
                                        num_updates / num_dependencies]

# calculate the median proportion of updated dependencies per package
num_dependencies_before_after_init_pr.median=
  num_dependencies_before_after_init_pr[, .(median_proportion_updates = 
                                              median(proportion_updates)),
                                        by = .(client_name_id,
                                               event)]

# plot
num_dependencies_before_after_init_pr.median$x = ""
num_dependencies_before_after_init_pr.median$event =
  factor(num_dependencies_before_after_init_pr.median$event,
         levels = c("before_init_pr",
                    "after_init_pr"),
         ordered = T)
plot_violin(num_dependencies_before_after_init_pr.median, 
            ycol = "median_proportion_updates",
            xcol = "x",
            group = "event",
            trim = FALSE,
            split = TRUE) +
  scale_y_continuous(trans = "log1p",
                     name = "Median proportion of updated dependencies",
                     limits = c(0, 1),
                     labels = percent) +
  scale_x_discrete(name = "Client package releases") +
  scale_fill_grey(name = "Before\nor after\ninitial PR?",
                  start = 0.7,
                  end = 1,
                  breaks = c("before_init_pr",
                             "after_init_pr"),
                  labels = c("Before",
                             "After"))+
  theme_classic()

summary(num_dependencies_before_after_init_pr.median[event == "before_init_pr"]$median_proportion_updates)
summary(num_dependencies_before_after_init_pr.median[event == "after_init_pr"]$median_proportion_updates)

median(num_dependencies_before_after_init_pr.median[event == "after_init_pr"]$median_proportion_updates) /
  median(num_dependencies_before_after_init_pr.median[event == "before_init_pr"]$median_proportion_updates)

wilcox.test(num_dependencies_before_after_init_pr.median[event == "before_init_pr"]$median_proportion_updates,
            num_dependencies_before_after_init_pr.median[event == "after_init_pr"]$median_proportion_updates)
cliff.delta(num_dependencies_before_after_init_pr.median[event == "before_init_pr"]$median_proportion_updates,
            num_dependencies_before_after_init_pr.median[event == "after_init_pr"]$median_proportion_updates)

```

```{r}
# normalize by number of releases after and before the bot integration
num_releases_before_after_init_pr =
  num_dependencies_before_after_init_pr[, .(num_releases = .N),
                                        by = client_name_id]
normalized_num_dependencies_before_after_init_pr =
  merge(num_dependencies_before_after_init_pr,
        num_releases_before_after_init_pr,
        by = "client_name_id")

normalized_num_dependencies_before_after_init_pr[, normalized_proportion_updates :=
                                                   proportion_updates / num_releases]

```

How many releases of the provider are not tracked by the bot?

```{r not_tracked_provider_releases}

# How many providers are not tracked by the bot?

# Get dependencies that are updated at dependency release
provider_updates_at_dependency_release = 
  dependencies[dependency_resolved_version_semver %in%
                 c("major", "minor", "patch") &
                 dependency_resolved_version_change == "upgrade" &
                 dependency_resolution_type == "at_dependency_release" &
                 dependency_resolved_timestamp > "2017-01-01T00:00:00Z"]

# Select only client packages that closed their initial PR
provider_updates_at_dependency_release =
  provider_updates_at_dependency_release[client_name_id %in%
                                           init_pr[pr_state == "closed"]$init_pr_id]

issues[, .(issue_id,
           issue_dependency_name,
           issue_dependency_actual_version,
           issue_dependency_next_version)]

select_packages_with_closed_init_pr =
  init_pr

percent_tracked_dependencies = 
  length(intersect(unique(provider_updates_at_dependency_release$dependency_name),
                   unique(issues$issue_dependency_name))) /
  length(unique(provider_updates_at_dependency_release$dependency_name))

paste(
  percent(percent_tracked_dependencies),
  "of the provider packages have at least ",
  "one of its releases tracked by the bot."
)

# How many clients do update the provider without the bot opening an issue?
updates_tracked_by_bot = 
  merge(provider_updates_at_dependency_release,
        issues,
        by.x = c("client_name_id",
                 "dependency_name",
                 "dependency_previous_resolved_version"),
        by.y = c("issue_id",
                 "issue_dependency_name",
                 "issue_dependency_actual_version"))

updated_dependencies_at_dependency_release = 
  provider_updates_at_dependency_release[dependency_resolved_version_semver %in%
                                           c("major", "minor", "patch"),
                                         .GRP,
                                         by = .(client_name,
                                                dependency_name,
                                                dependency_previous_resolved_version)]

percent_tracked_dependency_releases =
  nrow(updates_tracked_by_bot) /
  nrow(updated_dependencies_at_dependency_release)

paste(
  percent(percent_tracked_dependency_releases),
  "of the provider releases are tracked by the bot."
)

paste(
  percent(nrow(updates_tracked_by_bot[issue_state == "closed"]) /
  nrow(updates_tracked_by_bot)), "of the provider releases tracked",
  "by the bot are closed."
)

summary(updates_tracked_by_bot[issue_state == "closed"]$issue_num_comments)

```
