---
title: "WS-RQ1"
author: "Filipe Cogo"
date: "17/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 
"/scratch/filipe-cogo/wip-19-filipe-npm_greenkeeper_build_failures-scripts")
```

## Load external scripts

```{r load_external_scripts, echo=FALSE}

source("plotter.R")

```

## Load libraries

```{r load_libraries, include=FALSE, echo=FALSE}

library(data.table)
library(lubridate)
library(scales)
library(ggplot2)
library(stringr)
library(effsize)

```

## Read dataset

Reads two different data sets. While `releases` is the data about all package's releases, `dependencies` is the data about the dependencies of each package. Although `dependencies` also stores data about package's releases, any release of a package that has no valid dependency is not present in `dependencies`.

```{r read_data_set, include=FALSE, echo = FALSE}

issues = 
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_issues.csv",
        nThread = 80)

dependencies = 
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_dependencies_analysis.csv",
        nThread = 80)

init_pr = 
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_first_pull_request.csv",
        nThread = 80)

init_pr_events =
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_events_first_pull_request.csv",
        nThread = 80)

init_pr_commits =
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_first_pull_request_commits.csv",
        nThread = 80)

package_names =
  fread("../wip-19-filipe-npm_greenkeeper_build_failures-data/2019-07-14/greenkeeper_package_names.csv",
        nThread = 80)

paste("There are more package names than dependencies,",
      "since only packages with more than 100 commits",
      "are considered.")

```

# Link datasets

```{r link_dataset}


package_names[, package_id := 
                str_match(package_gh_url,
                          "^https://github\\.com/(.*?)/$")[,2]]

init_pr[, init_pr_id := 
          str_match(pr_repo_url,
                    "^https://api.github.com/repos/(.*?)$")[,2]]

init_pr_events[, init_pr_event_id :=
                 str_match(event_issue_url,
                    "^https://api.github.com/repos/(.*?)/issues/.*?$")[,2]]

init_pr_commits[, commit_event_id := 
                  str_match(commit_event_url,
                            "^https://api.github.com/repos/(.*?)/issues/.*?$")[,2]]

issues[, issue_id := 
         str_match(issue_repo_url,
                    "^https://api.github.com/repos/(.*?)$")[,2]
         ]

dependencies[, client_name_id := 
               str_replace(client_name,
                           "@",
                           "/")]

```

How many files are modified in the commits refer to the initial PR?

```{r}

summary(init_pr_commits[, .(num_files = .N),
                        by = commit_sha]$num_files)

```

What is the size of the commits that refer to the initial PR?

```{r}

summary(init_pr_commits[, .(num_modified_lines = sum(commit_stats_total)),
                        by = commit_sha]$num_modified_lines)

```

How many initial PRs are merged?

```{r}

init_pr_events_merged =
  init_pr_events[, .(has_merged = 
                       ifelse("merged" %in% event_description, T, F)),
                 by = event_issue_url]

nrow(init_pr_events_merged[has_merged == TRUE]) /
  nrow(init_pr_events_merged)

```

How many time to merge the initial PR?

```{r}

merged_init_pr = 
  merge(init_pr,
        init_pr_events[event_description == "merged"],
        by.x = "pr_url",
        by.y = "event_issue_url")

time_to_merge_init_pr = 
  merged_init_pr[, .(pr_url,
                     time_to_merge =
                       difftime(ymd_hms(event_created_at),
                                ymd_hms(pr_created_at),
                                unit = "hours"))]

ggplot(time_to_merge_init_pr,
       aes(x = "",
           y = as.numeric(time_to_merge))) +
  geom_violin(fill = "grey") +
  geom_boxplot(fill = "white",
               width = 0.05) +
  scale_y_log10(name = "Time to merge (hours)",
                labels = trans_format("log10",
                                      math_format(10^.x))) +
  scale_x_discrete(name = "Merged initial pull-requests") +
  theme_classic() +
  theme(axis.ticks.x = element_blank())

```

Does the initial pull request require a merge conflict to be resolved?

```{r}

View(merge(init_pr,
           init_pr_events,
           by.x = "pr_id",
           by.y = "event_issue_id"))

```